%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[normalem]{ulem}
\usepackage{tabularx}
\usepackage{calc}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubSubheadingLeft}[2]{
  \begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
  \end{description}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}}
\newcommand{\resumeItemListStart}{
\begin{itemize}}
    \newcommand{\resumeItemListEnd}{
  \end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Eliah Reeves} \\ \vspace{1pt}
  \small (916) 382-2329 $|$ \href{mailto:erreeves@ucsc.edu}{\uline{erreeves@ucsc.edu}} $|$
  \href{https://www.linkedin.com/in/eliah-reeves/}{\uline{linkedin.com/in/eliah-reeves}} $|$
  \href{https://github.com/nunibye}{\uline{github.com/nunibye}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of California, Santa Cruz}{ September 2022 -- June 2025}
{B.S. in Computer Engineering, with a minor in Computer Science, 3.97 GPA}{Santa Cruz, CA}
\resumeSubSubheadingLeft{Coursework:}{Parallel and Concurrent Programming, Computer System Design, Data Structures and Algorithms, Computer Architecture, VLSI, Verilog to Silicon: A graduate design project}

\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Student Assistant - Engineering and Architectural Sciences}{ July 2024 -- Present}
{California Department of Water Resources - Electrical Engineering Services}{ Sacramento, CA}
\resumeItemListStart
\resumeItem{Developed and implemented a Power BI dashboard integrated with Oracle Database to monitor maintenance across 26 bulk energy system facilities, tracking 6,500+ protective devices. Eliminated 24 monthly engineering hours and generating an estimated \$42,000 annual cost savings for government operations.}
\resumeItem{Created MATLAB Simulink model of synchronous machines based on IEEE standards to improve power grid reliability and ensure NERC compliance.}
\resumeItem{Prototyped a React/TypeScript web application to automate and streamline equipment test report management, reducing report processing time significantly and improving data accuracy.}
\resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Software Engineer}{ February 2024 -- May 2024}
{College Sauce - Social Media Startup}{ Santa Barbara, CA}
\resumeItemListStart
\resumeItem{Architected and implemented real-time messaging features for a college social networking app serving 4,500+ UC Santa Barbara students. Utilized Flutter, Firebase and PostgreSQL.}
\resumeItem{Collaborated with an interdisciplinary and international team of designers, marketers, and developers.}
\resumeItemListEnd

\resumeSubheading
{Software Engineering Intern}{ June 2023 -- September 2023}
{B\&K Precision Corporation}{ Yorba Linda, CA}
\resumeItemListStart
\resumeItem{Designed and launched cross-platform mobile and web application for elementary circuit analysis and general electronics calculations.}
\resumeItem{Developed a LabView driver/interface for a commercial DC Resistance meter.}
\resumeItem{Worked collaboratively to fine-tune user experience on a data acquisition platform before product launch.}
\resumeItemListEnd

\resumeSubheading
{Youth Climbing Instructor}{ August 2021 -- July 2022}
{Granite Arch Climbing Center}{ Rancho Cordova, CA}
\resumeItemListStart
\resumeItem{Instructed approximately 170 kids ages 5 to 18 in safe rock climbing techniques.}
\resumeItem{Created lesson plans to encourage the students to challenge themselves, while having fun.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{UCSC Menu App} $|$ \emph{Flutter, Firebase, Python, Go, AdMob}}{ October 2022 -- Present}
\resumeItemListStart
\resumeItem{Codevelop, maintain, and monetize an app with $>$3k downloads.}
\resumeItem{Use web scraping techniques and 3rd party API integration to provide a unified platform for all dining hall information including hours, menus, nutrition data, current occupancy, and payment.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Eko Social Media Network} $|$ \emph{Flutter, Firebase, Go, Google Cloud Platform}}{ July 2023 -- March 2024}
\resumeItemListStart
\resumeItem{Lead a team to develop a cross-platform social media network with a small, but active user base.}
\resumeItem{Features include: account control, user search, public messages, group chats, and personalized notifications.}
\resumeItem{Android, IOS, and Web platforms fully supported.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{PeerGrader Grading Software} $|$ \emph{Next.js, React, TypeScript, PostgreSQL, Scrum}}{ April 2024 -- Present}
\resumeItemListStart
\resumeItem{Working with a team to build a platform for peer feedback and grading.}
\resumeItem{Designed in collaboration with UCSC professor.}

\resumeItemListEnd
\resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{
        \textbf{Languages}{: C/C++, Python, Dart, SQL (Postgres \& Oracle), TypeScript, MATLAB, Verilog} \\
        \textbf{Frameworks}{: Flutter, React, Node.js, Next.js} \\
        \textbf{Services}{: Google Cloud Platform, Firebase, Supabase, Google Play Console, Apple Developer, AdMob} \\
    \textbf{Developer Tools}{: Git, Docker}\\}}
\end{itemize}


%-------------------------------------------
\end{document}